### 2015-10-16 committee_report/committee_report.tex
minor edit

Secondly, the obesity-specific genes specific to each cancer type were not checked with the BMI values of the samples.
The results presented here only showed the association of the metagene (created from a different cancer type and data) with the BMI value and status, and it would be good to double-check whether the expression of the genes show any correlation with the BMI of the samples in other cancer types.

>>>>

Secondly, the obesity-specific genes specific to each cancer type were not checked with the BMI values of the samples.
The results presented here only showed the association of the metagene, created from a different cancer type and data (Creighton \textit{et al.} and Fuentes-Mattei \textit{et al.} data), with the BMI value and status, and it would be good to double-check whether the expression of the genes show any correlation with the BMI of the samples in other cancer types.
